---
title: 'The Gini Coefficient under Binary Classification Problems'
subtitle: 'Theory and Practice'
author: "Harel Lustiger"
date: "October, 2017"
output: 
  ioslides_presentation: 
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Objective and Key Points

## Context

**Featured Prediction Competition:**   
[Porto Seguro’s Safe Driver Prediction](https://www.kaggle.com/c/porto-seguro-safe-driver-prediction).

**Problem:**  
Predict if a driver will file an insurance claim next year.

**Objective:**  
Maximize the (Normalized ) Gini Coefficient. 

**Prediction Type**
Classificaton with emphasize on *ranking classifiers*.

## Main Points

1. What are the relationships between Gini and and other criteria?
2. How does Gini behaive under unbalanced target variable?
3. How can we elicit more infromation from Gini?

## Key Attributes of the Target Variable

* The target variable has two states  
* The target variable is skewed.

## Assumptions

The train and test sets were drawn from the same **underlying distribution**.

IMAGE

Projecting the data into 2D space, and visual inspection suggest that this 
assumption is valid.


## Narrative

1. Key observation about the target variable (+hidden assumption)
2. Ontology of Performance Measures (where AUC, F-Score and why would would we Gini)
    * Graphical Preformance Measures
    * Ranking Performance Measures vs. Confusion Table
    * Performance Measures for Unbalaned target variable
    * SELECTED PERFORMANCE MEASUREAS ATTRIBUTE TABLE (Comparison)
3. 

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

