---
title: "Reconstructing Kaggle 1st Place Winning Solution"
subtitle: "80% `tidyverse` compatible"
subject: "Porto Seguro’s Safe Driver Prediction"
author: "Harel Lustiger"
date: "Dec 2017"
output: html_notebook
---

```{r new_session, echo=FALSE, message=FALSE, warning=FALSE}
rm(list = ls()); cat("\014")
```

# Load Packages

```{r load_libraries, echo=TRUE, message=FALSE, warning=FALSE}
library("tidyverse")
library("recipes")
library("rsample")
library("yardstick")
library("purrr")
library("caret")
```


# Import Data

In this dataset, each variable name contains designations about its type and 
group. Thus, the strategy is:

1. Get the data with `R` best guess
2. Extract the variable metadata held in the columns' names 
(as prefix/postfix/suffix) and use it for semi-automatic type-conversion. 

## Get the Data

The [data description in Kaggles]()https://www.kaggle.com/c/porto-seguro-safe-driver-prediction/data)
states that $-1$ represent missing values.
However, the author of this solution declers he didn't change these values.
Therefore, to be consistent with this solution we don't explicitly treat $-1$ as 
NA when the data is loaded.

```{r import_data, echo=TRUE, message=FALSE, warning=FALSE}
PATHS = list()
PATHS[["train"]] = file.path(dirname(getwd()),"data","train.zip")
PATHS[["test"]]= file.path(dirname(getwd()),"data","test.zip")
  
DATASETS = list()
DATASETS[["train"]] = read_csv(PATHS[["train"]], na=c("","NA"), n_max=1e3)
DATASETS[["test"]] = read_csv(PATHS[["test"]], na=c("","NA"), n_max=1e3)
  
tidy_data = bind_rows(list(train=DATASETS[["train"]], test=DATASETS[["test"]]),
                      .id="set")

y_name = "target"
```

## Parse the Data

```{r extracting_variables_groups_and_types, message=FALSE, warning=FALSE}
# 1. Extract variables types from their names
col_metadata = data.frame(name=colnames(tidy_data), stringsAsFactors=FALSE)
col_metadata %<>%
    # 1.1 Drop the 'set' row
    filter(name!="set") %>%
    # 1.1 Create new columns to hold the variables' metadata
    separate("name", into=c("prefix","group","number","type"), remove=F) %>%
    # 1.2 The metadata has irrelevant information which we discard
    select(-prefix, -number) %>%
    # By default the dataset creator omitted numeric variables designation. 
    # As a result, numeric variables are assigned with NAs.
    # 1.3 Replace NAs under the type col with "num".
    replace_na(list(type="num"))
  
# 2. Map the original type names with r known types
col_metadata[["type"]] = 
    sapply(col_metadata[["type"]], recode, 
           num="as.numeric", cat="as.factor", bin="as.logical")
  
# 3. Define the target variable to be binary
col_metadata[2,"type"] = "as.logical"
  
# 4. Set the data set variables types
for(j in 1:nrow(col_metadata)){
    col_name = col_metadata[j,"name"]
    col_type = col_metadata[j,"type"]
    # Match between the metadata and data set col numbers
    m = which(colnames(tidy_data) %in% col_name)
    # If the metadata doesn't fit any of the provided data set cols then skip it
    if(!m) next
    # Set the col data type
    tidy_data = tidy_data %>% mutate_at(m, col_type)
}
```


# Data Preprocessing

```{r feature_engineering, message=FALSE, warning=FALSE}
options(na.action='na.pass')

# 1. Drop the *calc variables group
tidy_data = tidy_data %>% select(-matches('.+_calc_.+$'))

# 2. Data Transformations
# 2.1 An Initial Recipe: declare the variables and their roles 
recipe_obj <- recipe(target ~ ., data=tidy_data)
recipe_obj <- recipe_obj %>%
    add_role(id, new_role="id variable") %>%
    add_role(set, new_role="splitting variable")
# 2.2 Preprocessing Steps
recipe_obj <- recipe_obj %>% 
    # 2.2.1 Individual transformations for skewness and other issues
    # 2.2.1.1 Yeo-Johnson Transformation
    step_YeoJohnson(all_numeric(), -id, na.rm=TRUE) %>% 
    # 2.2.1.2 Centering and Scaling Numeric Data
    step_center(all_numeric(), -id) %>%
    step_scale(all_numeric(), -id) %>%
    # 2.2.2 Creating Dummy Variables
    step_dummy(all_nominal(), -set)
# 2.3 Estimate the recipe statistics
recipe_obj <- recipe_obj %>% prep(training=tidy_data)
# 2.4 Apply the recipe to the data set
tidy_data = bake(recipe_obj, newdata=tidy_data)
  
options(na.action='na.omit')
``` 

# Building an AutoEncoder


# Define a Simple 5-fold Cross Validation 

1. Revert back to the original train/test split
2. Create a 5-Fold CV object from the train set

```{r split_the_data}
# Revert back to the original train/test split
tidy_train = tidy_data %>% filter(set %in% "train") %>% select(-set)
tidy_test = tidy_data %>% filter(set %in% "test") %>% select(-set)
  
# Create a 5-Fold CV object from the train set
set.seed(1309)
rsample_obj <- vfold_cv(tidy_train, V=5, repeats=1)
```

# Modeling

First, for convenience, we create a formula object that will be used later:

```{r modeling_formula}
model_formula <- paste(y_name,"~ . -id")
```

Second, we create a wrapper function that will, for each resample:

1. obtain the analysis data set (i.e. the 80% used for modeling)
2. fit a lightgbm model
3. predict the assessment data (the other 20% not used for the model) using the 
`broom` package
4. determine if each sample was predicted correctly.
  
```{r modeling}
#' @param splits is the `rsplit` object with the 80/20 partition
holdout_results <- function(splits, ...) {
    # Get the data sets
    tidy_analysis = analysis(splits)
    tidy_assessment = assessment(splits)
    # Fit the model to the 80%
    mod <- glm(..., data=tidy_analysis, family=binomial)
    # Predict the other 20%
    Class1 = predict.glm(mod, newdata=tidy_assessment, type="response")
    Class2 = 1-Class1
    res = data.frame(truth=factor(tidy_assessment[[y_name]]),
                     Class1=Class1, Class2=Class2)
    #   truth   Class1          Class2
    # 1 FALSE   1.474315e-11    1.00000000
    # 2 FALSE   6.876193e-01    0.31238066
    # 3 FALSE   2.220446e-16    1.00000000
    # 4 FALSE   2.220446e-16    1.00000000
    return(res)
}# holdout_results()
```

```{r modeling_insanity_check, eval=FALSE, message=TRUE, warning=TRUE, include=FALSE}
single_model <- holdout_results(rsample_obj$splits[[1]],  model_formula)
roc_auc(single_model, truth=truth, Class1)
```

# Model Assessment

```{r model_evaluation, message=FALSE, warning=FALSE}
rsample_obj$results <- map(rsample_obj$splits,
                      holdout_results,
                      model_formula)
```

## Calculate the Gini Coefficient

```{r AUC}
rsample_obj$AUC = map_dbl(rsample_obj$results, roc_auc, truth=truth, Class1)
rsample_obj$AUC = ifelse(rsample_obj$AUC>0.5,rsample_obj$AUC,1-rsample_obj$AUC)
rsample_obj$Gini = rsample_obj$AUC * 2 - 1

summary(rsample_obj$Gini)
```

Random Forest Benchmark: 0.24529





https://docs.google.com/document/d/1tosvfWMkfW1-UkEQ1LL66PlFTmVZfXkbP0Dl1x5KcvA/edit#
https://www.kaggle.com/c/porto-seguro-safe-driver-prediction/discussion/44629
https://keras.rstudio.com/articles/examples/variational_autoencoder.html
https://www.udemy.com/deeplearning/learn/v4/content



